---
title: "Investigator Portfolio"
author: "Benjamin T. Carter, PhD"
date: "Generated: `r Sys.time()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
  powerpoint_presentation:
    df_print: "kable"
    slide_level: 2
    # reference_doc: "style_template.pptx"
params:
  format: "markdown"
  ar_stratify: "race"
  year: 2021
  author: "Benjamin T Carter"
---

```{r echo=FALSE, include=FALSE}
knitr::opts_chunk$set(message=FALSE, 
                      error=FALSE, 
                      warning=FALSE, 
                      echo = FALSE)

# load libraries
list.of.packages <- c("tidyverse", 
                      "ggplot2")

# compare the list to the installed packages list and add missing packages to new list
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# install missing packages
if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
meh <- lapply(list.of.packages,library,character.only = TRUE)
rm(meh)

if (params$format == "markdown"){
  cg_format <- "markdown"
} else {
  cg_format <- "html"
}

REP_YEAR <- params$year
author_id <- params$author
```

# Questions this should answer:

1. How many proposals have I completed?
2. How many grants have I submitted? Won?
3. How many databases have I created or opened?
4. How many analyses have I completed?
5. How many manuscripts have I authored?
6. How many manuscripts have I supported?
7. How many publications have I produced?
8. How many publications have I supported?
7. How have I spent my time while doing the above?
8. How could I be more efficient?
9. How much is my work disseminated?
10. How effective is my dissemination?
11. Who are my coauthors?
12. Who cite's my work?

# 2021 Summary
```{r}



```

